### 2020-09-04 latex/vlp.tex
Added VLP images for l(theta)

\begin{figure}
   \centering
   % TODO: Inser the image of the optimal controller in the (q,p) plane: it
   % should just be 4 coloured quadrants (no spiral) representing squatting and
   % standing
   \caption{The time-optimal VLP controller from
   \cite{pumping_swing_standing_squatting} displayed in the
\((q,p)\)-plane.}\label{fig:vlp-optimal-controller-qp-plane}
\end{figure}

\begin{figure}
   \centering
   %TODO: Insert the image of the optimal controller as a function of theta;
   %that is, show l(theta) vs theta on ]-pi,pi] and show underline{l} and
   %overline{l} 
   \caption{The time-optimal VLP controller converted to a discontinuous
   function \(l(\theta)\).}\label{fig:vlp-optimal-controller}
\end{figure}

>>>>

\begin{figure}
   \centering
   \includestandalone[width=0.5\textwidth]{images/vlp_optimal_controller_qp_plane}
   \caption{The representation of the time-optimal controller for a standing
      swing in the \((q,p)\)-plane. As per 
      \cite{pumping_swing_standing_squatting}, the red region corresponds to
      squatting and the blue region corresponds to standing.}
      \label{fig:vlp-optimal-controller-qp-plane}
\end{figure}

\begin{figure}
   \centering
   \includestandalone[width=0.5\textwidth]{images/vlp_optimal_controller}
   \caption{The time-optimal VLP controller converted to a discontinuous
   function \(l(\theta)\), where \(\theta := \arctan_2(p,q)\).}\label{fig:vlp-optimal-controller}
\end{figure}
